### 2018-05-18 paper/paper.tex
minor updates to bayesian analysis

To evaluate the effect of the discourse status of the generalization on the at-issueness of the prejacent, we fit a Bayesian binomial mixed effects model with uninformative priors using the R package \verb|brms| \citep{buerkner2017}.\footnote{We fit a Bayesian binomial mixed effects model rather than a \jt{regular?} one because \jt{reasons}. In fact, when we fit binomial mixed effects models, predicting response from a fixed effect of the discourse status of the generalizations, the models only converged if we included either a random by-adjective intercept or a random by-participant intercept, but not both. } The model predicted the log odds of `yes' over `no' ratings from a fixed effect of the discourse status of the generalization (with `neutral generalization' as the reference level). We included the maximal random effects structure justified by the design: random intercepts for item (capturing differences in projectivity between items), adjective (capturing differences in projectivity between adjectives), and participant (capturing differences in projectivity between participants) as well as random by-adjective and by-participant slopes for discourse status (capturing that the effect of discourse status may vary by adjective and participant). Four chains converged after 2000 iterations each (warmup = 1000, \(\hat{R}=1\) for all estimated parameters).

>>>>

To evaluate the effect of the discourse status of the generalization on the at-issueness of the prejacent, we fit a Bayesian binomial mixed effects model with uninformative priors using the R package \verb|brms| \citep{buerkner2017}.\footnote{We fit a Bayesian binomial mixed effects model rather than a \jt{regular?} one because \jt{reasons}. In fact, when we fit binomial mixed effects models, predicting response from a fixed effect of the discourse status of the generalizations, the models only converged if we included either a random by-adjective intercept or a random by-participant intercept, but not both. } The model predicted the log odds of `yes' over `no' ratings from a fixed effect of the discourse status of the generalization (with `neutral generalization' as the reference level). We included the maximal random effects structure justified by the design: random intercepts for item (capturing random differences in projectivity between items) and participant (capturing random differences in projectivity between participants) as well as random by-participant slopes for discourse status (capturing that the effect of discourse status may vary by participant). Four chains converged after 2000 iterations each (warmup = 1000, \(\hat{R}=1\) for all estimated parameters).
